A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-05-15 paper.Rmd
remove hyperlink to tidy tuesday repo, as it now has a proper bib reference.

Below is an example data dictionary table taken from the [Tidy Tuesday repository on incarceration trends](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-01-22) [@tidy-tuesday-incarcerate]. This includes information on the variable the class (type) of the variable, and a longer description of the variable.

>>>>

Below is an example data dictionary table taken from the Tidy Tuesday repository on incarceration trends [@tidy-tuesday-incarcerate]. This includes information on the variable the class (type) of the variable, and a longer description of the variable.
